Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-11 paper/main.tex
Started concluding

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently? Criticize
% ourselves.

@@

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% A somewhat short conclusion summing up what has been done, and results and
% discussion
%
% We had hoped to have contributed more to the Open Source project that
% Tahoe-LAFS is.

>>>>

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsistencies in the numbers, and try to explain them.
% Time spent not hashing varies because: Variable use of CPU regs?
%
% Compare our results with general (SUPERCOP) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% How much gain can Tahoe-LAFS get by switching to SHA-3?
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently? Criticize
% ourselves.

@@

% This chapter should contain:
% -----------------------------------------------------------
% A somewhat short conclusion summing up what has been done, and results and
% discussion

We had hoped to contribute more to the Open Source project Tahoe-LAFS, when
starting on our assignment. It was early evident that implementing a new
capability was out of scope, since creating Python bindings for and trying out
new implementations was prioritized.

Perhaps the most important finding in this project, is that the SUPERCOP
benchmarking indeed drives the development of new and better implementations
forward, but since the SUPERCOP \ac{API} does not conform to the \ac{NIST}
\ac{API}, the developers leave important functionality out (i.e.
{\verb update() }), and hence make it difficult for people who wish to try out
and test the remaining \ac{SHA}-3 candidates.
